---
title: "Assignment_1_Anita_Putaturo"
author: "Anita Putaturo"
date: "2025-09-05"
output: pdf_document
---


```{r}

options(repos = c(CRAN = "https://cloud.r-project.org"))
library(rmarkdown)
library(ggplot2)
```


1. The dataset I chose is from Kaggle: https://www.kaggle.com/datasets/rohitgrewal/airlines-flights-data
The data in this dataset has a decent mix of quantitative and qualitative variables.

2. Importing the dataset and naming it "airlines"
```{r}
airlines<- read.csv("C:\\Users\\aputa\\OneDrive\\Documents\\Graduate Courses\\Fundamentals of Machine Learning F25\\Homework Assignments\\Assignment 1 Dataset\\airline_data.csv")
```


3. Printing the dataset
```{r}
print(airlines)
```

3. Printing descriptive statistics for numerical variables
```{r}
summary(airlines[,c("duration", "price")])

```
Printing descriptive statistics for categorical variables: count of airline per arrival time category
```{r}
table(airlines$airline, airlines$arrival_time)
```
4. Add a new column in the table called "duration_mins" to convert the duration from hours to minutes.
```{r}
airlines$duration_mins<- airlines$duration*60
print(airlines)

```

5. Plotting a histogram of duration in minutes. Data is skewed
```{r}
hist(airlines$duration,
     main = "Histogram of Duration in Hours",
     xlab = "Hours",
     col = "lightblue")
```

Scatter plot
```{r}
plot(airlines$duration, airlines$price,
     main = "Price versus Duration",
     xlab = "price",
     ylab = "Flight Duration (hours)")
```




